\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 classification.tex

One direct application of trip data is unsupervised learning. Previous works have focused on identifying travel modes or purpose of trip from different sources of data, most notably: survey data, GPS data and mobile phone data~\cite{ODMobileData, ClusteringGPS}. Determining the distribution of travel modes is one of the fundamental steps in the four-stage model: an essential traffic modelling methodology for transportation planning~\cite{FourStepModel}. Although number-plate data has been used in~\cite{Clustering}, to identify different categories of trips, these do not differentiate between private or public travel modes and focus for the most part on when the trips occurred. Therefore, we aim to identify groups of vehicles with similar trip patterns based on frequency and diversity of travel. This can be private vehicles, such as work-home commuters, transit vehicles like buses and taxis, or other types of vehicles such as delivery trucks.
%This in turn, may enable trip modes to be estimated
However, due to its limited coverage of the road network, it is not clear how well ANPR data can capture much the travel characteristics necessary to accurately describe the different groups.

>>>>

One direct application of trip data is unsupervised learning. In this section we identify groups of vehicles with similar trip patterns based on frequency and diversity of travel. Clusters can represent private vehicles, such as work-home commuters, transit vehicles like buses and taxis, or other types of vehicles such as delivery trucks.
%This in turn, may enable trip modes to be estimated
%However, due to its limited coverage of the road network, it is not clear how well ANPR data can capture much the travel characteristics necessary to accurately describe the different groups.

### 2018-02-01 dataset.tex
Fixed some grammar mistakes and added abstract

\begin{figure}[t]
\centering
\includegraphics[width=.95\linewidth]{ANPR-overview.pdf}
\caption{Automatic number plate recognition system overview.}
\label{fig:anpr-overview}
\end{figure}

@@

\begin{table}[ht]
\centering
\tabcolsep=0.17cm
\small
\begin{tabular}{c c c c c}
  \hline
  Vehicle & Camera & Timestamp & \thead{Clock \\Error} & Confidence \\
  \hline
  169239 & 1031 & 1454284800.26 &   0 & 100 \\
  12862943 & 18 & 1454284800.97 &   8 &  61 \\
  16243894 & 22 & 1454284801.46 &   6 &  86 \\
  4817789 & 52 & 1454284803.43 &  13 &  94 \\
  5503486 & 110 & 1454284802.19 &  22 &  91 \\
  15244177 & 115 & 1454284802.83 &  18 &  87 \\
  6756787 & 146 & 1454284801.53 &  22 &  99 \\
  8487265 & 2 & 1454284803.88 &  10 &  93 \\
   \hline
\end{tabular}
\caption{Sample of number plate data. Clock error is given in milliseconds and confidence as a percentile value.}
\label{t:np_data_example}
\end{table}

{\color{red}{\color{blue}Much of this paragraph should be in related work}
The main use of ANPR data for the UTMC is estimating average journey times for selected links in the road network. Furthermore, several authors have extensively researched how to use number-plate data as an extension to link counts for estimating origin-destination matrices and link flows~\cite{Castillo2010, Castillo2008, Hazelton2012}. However, very few works have focused on analysing individual or collective travel patterns from number-plate data, particularly across extended periods of time. Moreover, there is no consistent conceptual and analytical framework for transforming number plate data into a historical sequence of trips for each vehicle. Finally, we believe that trip data, properly identified from number-plate data, has the potential to unlock a number of new applications for urban traffic control and law enforcement. Thus, in the following section we present a conceptual methodology for grouping multiple camera observations of the same vehicle into one or several trips of that vehicle.
}

>>>>

@@

\begin{table}[ht]
\centering
\tabcolsep=0.17cm
\small
\begin{tabular}{c c c c c}
  \hline
  Vehicle & Camera & Timestamp & \thead{Clock \\Error} & Confidence \\
  \hline
  169239 & 1031 & 1454284800.26 &   0 & 100 \\
  12862943 & 18 & 1454284800.97 &   8 &  61 \\
  16243894 & 22 & 1454284801.46 &   6 &  86 \\
  4817789 & 52 & 1454284803.43 &  13 &  94 \\
  5503486 & 110 & 1454284802.19 &  22 &  91 \\
  15244177 & 115 & 1454284802.83 &  18 &  87 \\
   \hline
\end{tabular}
\caption{Sample of number plate data. Clock error is given in milliseconds and confidence as a percentile value.}
\label{t:np_data_example}
%\vspace{-2cm}
\end{table}

### 2018-02-01 intro.tex

%Even though the cameras only cover a very small subset of the entire road network, the network of cameras provides a valuable time-varying picture of travel demands and traffic states.

In ~\cite{Castillo2008}, the authors used partial trip information from plate number scans to compute travel demands, in the form of a trip matrix, and estimate link flows from a set of constraints composed of traffic conservation laws, prior knowledge and path flow disaggregation techniques, such as Stochastic User Equilibrium (SUE).

@@

Uses of trip data for understandint travel demands / traffic prediction

Studies about best placement of cameras

Number plate data is not as popular, for urban traffic monitoring and prediction , as other sources of data, namely GPS traces or floating vehicle data.
Previous works trips from GPS traces, .

%Therefore, number plate scans provide additional trip information, besides simple link counts, that has

 %estimating travel demands and traffic states. extended traditional methods of  travel demands

Although significant research has gone into identifying trips from GPS traces, to the best of our knowledge, little research has gone into doing so with number plate data. Therefore, the contributions of this paper are twofold:

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=.95\linewidth]{ANPR-overview.pdf}
\caption{Automatic number plate recognition system overview.}
\label{fig:anpr-overview}
\end{figure}

The main use of ANPR data for the UTMC is estimating average journey times for selected or sensitive links in the road network. Furthermore, several authors have extensively researched how to use number-plate data as an extension to link counts for estimating origin-destination matrices and link flows~\cite{Castillo2010, Castillo2008, Hazelton2012}. However, very few works have focused on analysing individual or collective travel patterns from number-plate data, particularly across extended periods of time. Moreover, there is no consistent conceptual and analytical framework for transforming number plate data into a historical sequence of trips for each vehicle. Finally, we believe that trip data, properly identified from number-plate data, has the potential to unlock a number of new applications for urban traffic control and law enforcement. Thus, in section~\ref{s.trips} we present a conceptual methodology for grouping multiple camera observations of the same vehicle into one or several trips of that vehicle.

Determining the distribution of travel modes is one of the fundamental steps in the four-stage model: an essential traffic modelling methodology for transportation planning~\cite{FourStepModel}. Previous works have used trip information derived from different sources of data to identify travel mode or purpose of trip. More notably, survey data, floating car data and mobile phone data have been used~\cite{ODMobileData, ClusteringGPS}.  Although number plate data has been used in~\cite{Clustering}, to identify different categories of trips, the authors do not differentiate between private or public travel modes and focus instead on categorising trips by time of occurrence. Hence, in section~\ref{s.classification} we apply the \emph{k-means} clustering algorithm to derived trip data and based on the results, we discuss the limitations of proposed methods and that of ANPR data.

@@

% {\color{red}Uses of trip data for understanding travel demands / traffic prediction
%
% Studies about best placement of cameras
%
% Number plate data is not as popular, for urban traffic monitoring and prediction, as other sources of data, namely GPS traces or floating vehicle data.
% Previous works trips from GPS traces, .
%
% %Therefore, number plate scans provide additional trip information, besides simple link counts, that has
%
%  %estimating travel demands and traffic states. extended traditional methods of  travel demands
%
%
% Although significant research has gone into identifying trips from GPS traces, to the best of our knowledge, little research has gone into doing so with number plate data. Therefore, the contributions of this paper are twofold:
